\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/conclusion.tex
resolve conflict

Leveraging the new features of USB 3.x~\cite{usb30,usb31,usb32}, we explore a
new attack scheme named \tool and three attack modes. Each of these three modes
has its own strength and use scenarios. The HID emulator mode largely extends the
original BadUSB and successfully bypasses existing defenses. The video capture mode proved practical and powerful in the user study, as it extracts
victim's sensitive information in a stealthy way. The fully control mode
archives the complete hijack of the target device, allowing us to perform various
types of subsequent attacks. By experimenting \tool with mobile phones, tablets,
and PCs, we further test its ability under different modes and shows it can
bypass defenses such as GoodUSB~\cite{tian2015defending}. In our user study, we
obtain and analyze video stream extracted from 10 participants with \tool,
which demonstrates its capability in a real-life scenario. In the end, we
propose a new defense scheme named \textit{isolated UI rendering}, which can
effectively stop our \tool.

>>>>

Leveraging the new features of USB 3.x~\cite{usb30,usb31,usb32}, we explore a
new attack scheme named \tool and three attack modes. Each of these three modes
has its own strength and use scenarios. The HID Emulation mode largely extends the
original BadUSB and successfully bypasses existing defenses. The video capture mode proved practical and powerful in the user study, as it extracts
victim's sensitive information in a stealthy way. The full control mode
archives the complete hijack of the target device, allowing us to perform various
types of subsequent attacks. By experimenting \tool with mobile phones, tablets,
and PCs, we further test its ability under different modes and shows it can
bypass defenses such as GoodUSB~\cite{tian2015defending}. In our user study, we
obtain and analyze video stream extracted from 10 participants with \tool,
which demonstrates its capability in a real-life scenario. In the end, we
propose a new defense scheme named \textit{isolated UI rendering}, which can
effectively stop our \tool.
